Manuscript

### 2019-01-10 manuscript_analysis.Rmd

>>>>

## Tests

```{r}
ccle_pearson_ttest_GE <- t.test(ccle_cor_res$Pearson_Corr_GE ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_GE <- paste0("t(", round(ccle_pearson_ttest_GE$parameter, 0), ") = ", round(ccle_pearson_ttest_GE$statistic, 2), ", p = ", round(ccle_pearson_ttest_GE$p.value, 2))
ccle_pearson_ttest_CN <- t.test(ccle_cor_res$Pearson_Corr_CN ~ ccle_cor_res$InG2P)
ccle_pearson_ttest_res_CN <- paste0("t(", round(ccle_pearson_ttest_CN$parameter, 0), ") = ", round(ccle_pearson_ttest_CN$statistic, 2), ", p = ", round(ccle_pearson_ttest_CN$p.value, 2))
ccle_spearman_ttest_GE <- t.test(ccle_cor_res$Spearman_Corr_GE ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_GE <- paste0("t(", round(ccle_spearman_ttest_GE$parameter, 0), ") = ", round(ccle_spearman_ttest_GE$statistic, 2), ", p = ", round(ccle_spearman_ttest_GE$p.value, 2))
ccle_spearman_ttest_CN <- t.test(ccle_cor_res$Spearman_Corr_CN ~ ccle_cor_res$InG2P)
ccle_spearman_ttest_res_CN <- paste0("t(", round(ccle_spearman_ttest_CN$parameter, 0), ") = ", round(ccle_spearman_ttest_CN$statistic, 2), ", p = ", formatC(ccle_spearman_ttest_CN$p.value, 2, format = "f"))

ctrp_pearson_ttest_GE <- t.test(ctrp_cor_res$Pearson_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_GE <- paste0("t(", round(ctrp_pearson_ttest_GE$parameter, 0), ") = ", round(ctrp_pearson_ttest_GE$statistic, 2), ", p ", ifelse(round(ctrp_pearson_ttest_GE$p.value, 3) == 0, "< 0.001", paste0("= ", round(ctrp_pearson_ttest_GE$p.value, 3))))
ctrp_pearson_ttest_CN <- t.test(ctrp_cor_res$Pearson_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_pearson_ttest_res_CN <- paste0("t(", round(ctrp_pearson_ttest_CN$parameter, 0), ") = ", round(ctrp_pearson_ttest_CN$statistic, 2), ", p = ", round(ctrp_pearson_ttest_CN$p.value, 3))
ctrp_spearman_ttest_GE <- t.test(ctrp_cor_res$Spearman_Corr_GE ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_GE <- paste0("t(", round(ctrp_spearman_ttest_GE$parameter, 0), ") = ", round(ctrp_spearman_ttest_GE$statistic, 2), ", p = ", round(ctrp_spearman_ttest_GE$p.value, 2))
ctrp_spearman_ttest_CN <- t.test(ctrp_cor_res$Spearman_Corr_CN ~ ctrp_cor_res$InG2P)
ctrp_spearman_ttest_res_CN <- paste0("t(", round(ctrp_spearman_ttest_CN$parameter, 0), ") = ", round(ctrp_spearman_ttest_CN$statistic, 2), ", p = ", round(ctrp_spearman_ttest_CN$p.value, 2))

gdsc_pearson_ttest_GE <- t.test(gdsc_cor_res$Pearson_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_GE <- paste0("t(", round(gdsc_pearson_ttest_GE$parameter, 0), ") = ", round(gdsc_pearson_ttest_GE$statistic, 2), ", p = ", round(gdsc_pearson_ttest_GE$p.value, 3))
gdsc_pearson_ttest_CN <- t.test(gdsc_cor_res$Pearson_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_pearson_ttest_res_CN <- paste0("t(", round(gdsc_pearson_ttest_CN$parameter, 0), ") = ", round(gdsc_pearson_ttest_CN$statistic, 2), ", p = ", round(gdsc_pearson_ttest_CN$p.value, 3))
gdsc_spearman_ttest_GE <- t.test(gdsc_cor_res$Spearman_Corr_GE ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_GE <- paste0("t(", round(gdsc_spearman_ttest_GE$parameter, 0), ") = ", round(gdsc_spearman_ttest_GE$statistic, 2), ", p = ", round(gdsc_spearman_ttest_GE$p.value, 2))
gdsc_spearman_ttest_CN <- t.test(gdsc_cor_res$Spearman_Corr_CN ~ gdsc_cor_res$InG2P)
gdsc_spearman_ttest_res_CN <- paste0("t(", round(gdsc_spearman_ttest_CN$parameter, 0), ") = ", round(gdsc_spearman_ttest_CN$statistic, 2), ", p = ", round(gdsc_spearman_ttest_CN$p.value, 2))

g2p_cor_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"), Pearson_Test_Results_GE = c(ccle_pearson_ttest_res_GE, ctrp_pearson_ttest_res_GE, gdsc_pearson_ttest_res_GE), Pearson_Test_Results_CN = c(ccle_pearson_ttest_res_CN, ctrp_pearson_ttest_res_CN, gdsc_pearson_ttest_res_CN), Spearman_Test_Results_GE = c(ccle_spearman_ttest_res_GE, ctrp_spearman_ttest_res_GE, gdsc_spearman_ttest_res_GE), Spearman_Test_Results_CN = c(ccle_spearman_ttest_res_CN, ctrp_spearman_ttest_res_CN, gdsc_spearman_ttest_res_CN))
```
